On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 tt_theorem.tex
12/5 evening.....

    \end{tabular}
    \caption{Direction into an entrance of a tunnel: (Left) straight, (Middle) obtuse, (Right) acute. The bead $w[i]$ is stabilized at an entrance and $w[i+1]$ is stabilized inside a tunnel.}
    \label{TTT_tunnel_direction}
  \end{center}
\end{figure}

>>>>

    \end{tabular}
    \caption{The three ways to enter a tunnel: (Left) straight, (Middle) obtuse, (Right) acute. The bead $w[i]$ is stabilized at the entrance and $w[i+1]$ is stabilized inside.}
    \label{TTT_tunnel_direction}
  \end{center}
\end{figure}
